\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-27 paper.tex
version 0.3.2.2

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\soulregister\cite7
\soulregister\ref7
\pagestyle{plain}

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.

Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[t]
\centering
\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v2}
\end{figure}

\subsubsection{Encoding Process}
The encoding process can be divided into two phases: important coding phase and global coding phase. We us RS code to generate both important parity sectors and global parity sectors.

\emph{Phase 1} Encode important data sectors based on Galois Field (GF) and generate $s$ groups of RS parity sectors labeled with $q_{i,j}$ and they are defined by equation \ref{q_ij}, where $\alpha$ is the coefficient in GF. According to Figure \ref{apcode-7222-v2}, Phase 1 use RS(5,3).
For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$

\textbf{Phase 2:} Generate $m$ parity chunks from $h+s$ chunks consist of data sectors and important parity sectors.

 , $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$

\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
\end{equation}
\begin{equation}
    \mathop{p_{i,j}}\limits_{i<t} = 
    \sum_{k=0}^{h-1} \alpha_k^{s+j+1} d_{i,k} +
    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j+1} q_{i,l}
\end{equation}
\begin{equation}
    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
    \sum_{k=0}^{n-m-1} \alpha_k^{s+j+1} d_{i,k}
\end{equation}

@@

\section{Evaluation}
\subsection{An Evaluation methodology}
\subsubsection{Erasure Codes in Our Comparisons}
\subsubsection{Platforms and Configurations}
\subsubsection{Metrics}
\subsubsection{Parameters and Assumption in Our Evaluation}

>>>>

%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
\soulregister\cite7
\soulregister\ref7
\pagestyle{plain}

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v2}
\end{figure}

A variety of erasure codes can be used for the encoding and decoding process of Approximate Codes. Here we only introduce our RS-based design as an example. 
\hl{Approximate Codes based on other erasure code schemes include XOR-based codes or MSR codes will be introduced in Section }\ref{evaluation}.

\subsubsection{Encoding Process}
The encoding process can be divided into two phases: important coding phase and global coding phase.

In \emph{phase 1}, we use RS$(h+s,h)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$. The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF). 
For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
As shown in the blod box in Figure \ref{apcode-7222-v2}, we use RS(5,3) in this phase.
\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
\end{equation}

In \emph{phase 2}, we use RS$(n,n-m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors. The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
As shown in orange chunks in Figure \ref{apcode-7222-v2}, we use RS(7,5) in this phase.

\begin{equation}\label{p_ij_1}
    \mathop{p_{i,j}}\limits_{i<t} = 
    \sum_{k=0}^{h-1} \alpha_k^{s+j+1} d_{i,k} +
    \sum_{l=0}^{s-1} \alpha_{l+h}^{s+j+1} q_{i,l}
\end{equation}
\begin{equation}\label{p_ij_2}
    \mathop{p_{i,j}}\limits_{i \geqslant t} = 
    \sum_{k=0}^{n-m-1} \alpha_k^{s+j+1} d_{i,k}
\end{equation}

@@

\section{Evaluation}\label{evaluation}
\subsection{An Evaluation methodology}
\subsubsection{Erasure Codes in Our Comparisons}
\subsubsection{Platforms and Configurations}
\subsubsection{Metrics}
\subsubsection{Parameters and Assumption in Our Evaluation}
